Exploiting the Social Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-26 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
Proceeding to case study

@@

\begin{itemize}
\item {\bf Likes} This relation describes the interaction between a user and
an individual in which a rating value is assigned this is represented by 
the {\tt rate} attribute. In the current application a user is allowed to rate
an individual multiple times, so the date of the interactions is also of
interest.

\item {\bf Knows} The relation connects two users that know each
other. This relation is "unique" meaning that it can not be repeated between a pair of nodes.

@@

\item {\bf Shared} When a user takes an individual from a friend's collection, this interactions 
is described by a {\tt share} relationship, between the user and the individual.

@@

Is important to notice that this model is still partial view of the IEC system,
and other models can could be used in practice when implementing the system. 
For instance a relational database can be used for the implementation of a
user profile and authentication module. Also a copy or cache of the population 
could be kept in a key-value store in memory for performance reasons. 
Nevertheless, the model can give important insights of the behavior of the 
system.

@@

We present in this section the results of a comparison between three versions
of the same IEC application. The goal of the experiment is to compare two 
gamification techniques to increase volunteer participation against a third 
without any thechnique applied.

>>>>

% Add something at the end linking with the next paragraph

@@

These relationships are expressed as edges in the graph. We use
several of them.

\begin{itemize}
\item {\bf Likes} This relation describes the interaction between a user and
an individual in which a rating value is assigned this is represented by 
the {\tt rate} attribute. In the current application a user is allowed to rate
an individual multiple times, so the date of the interactions is also of
interest.
%this is a bipartite graph them. - JJ

\item {\bf Knows} The relation connects two users that know each
other. This relation is "unique" meaning that it cannot be repeated
between a pair of nodes.  % Not too clear what you mean by that - JJ

@@

\item {\bf Shared} When a user takes an individual from a friend's collection, this interactions 
is described by a {\tt share} relationship between the user and the
individual.  % Still think that user and individual is confusing - JJ

@@

Is important to notice that this model is still a partial view of the IEC system,
and other models can could be used in practice when implementing the
system. % It is also a bipartite graph, which could be converted to a
% single-party graph with only one type of node.
% I don't think "collections" should be nodes too. They are simply
% attributes for an individual - JJ
For instance a relational database can be used for the implementation of a
user profile and authentication module. Also a copy or cache of the population 
could be kept in a key-value store in memory for performance reasons. 
Nevertheless, the model can give important insights of the behavior of the 
system.   % So what we have done here is this and that because... - JJ

@@

We present in this section the results of a comparison between three versions
of the same IEC application. The goal of the experiment is to compare two 
gamification techniques to increase volunteer participation against a third 
without any technique applied.
